Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-07 6-ModelPresentation.tex

Figure \ref{fig:MultilevelArchitecture} shows the overview of the multivel architecture designed to capture the two use cases described in Process Challenge.

>>>>

Figure \ref{fig:MultilevelArchitecture} shows the overview of the multivel architecture designed to capture the two use cases described in the Process Challenge.
